Sequential algorithms to split and merge ultra-high resolution 3D images

### 2017-07-28 paper.tex
Updates following discussion with Yongping

Three-dimensional images that exceed typical memory size are
increasingly found in a variety of disciplines. BigBrain, for
instance, is a 3D histological image of the human brain that
represents 1~TB of data organized in 3600 planes at full resolution
(1$\mu$m in-plane), and 76~GB at a 40$\mu$m isotropic resolution
commonly used in neurosciences~\cite{amunts2013bigbrain}. Other
examples found in medical imaging, our primary domain of interest,
include \todo{electromicroscopy,spectroscopy-francoise-peyrin}. As
such images would typically be processed on a computing cluster,
possibly using locality-aware file systems such as HDFS, software
libraries are needed to split and merge such images efficiently. We
introduce and compare a family of algorithms to address this problem
in a sequential environment made of a single storage disk. We are
aware of the need for parallel algorithms that would split and merge
images to and from an array of disks but we plan to describe such
algorithms in a subsequent paper based on the results of the present
one.

@@

@@

@@

>>>>

Three-dimensional images that exceed typical memory size are
increasingly found in a variety of disciplines. BigBrain, for
instance, is a 3D histological image of the human brain that
represents 1~TB of data organized in 3600 planes at full resolution
(1$\mu$m in-plane), and 76~GB at a 40$\mu$m isotropic resolution
commonly used in neurosciences~\cite{amunts2013bigbrain}. Other
examples found in medical imaging, our primary domain of interest,
include \todo{electromicroscopy,spectroscopy-francoise-peyrin}. As
such images would typically be processed on a computing cluster,
possibly using locality-aware file systems such as HDFS, software
libraries are needed to split and merge such images efficiently. We
introduce and compare a family of algorithms to address this problem
in a sequential environment made of a single storage disk. We are
aware of the need for parallel algorithms that would split and merge
images to and from an array of disks but we plan to describe such
algorithms in a subsequent paper based on the results of the present
one. \todo{
There is BigBrain-1 rescanned at 1 micron in the plane. So resolution
is 1x1x20, 7404 slices. If raw data are about 1Tb, then multiply by
100 for an estimation of the size of the new image. }

@@

\subsubsection{Cluster reads}

\subsubsection{Multiple reads}

\todo{Yongping: among other implementation techniques (e.g. dictionary
  vs list, etc), explain clearly and concisely what the calculation
  time covers.}

@@

Results discussion:
\begin{itemize}
\item Comment on calculation time.
\item Write time is higher than read time because use nibabel for writing but not reading.
\item It seems that the merge time is quite stable w.r.t the amount of available memory. This is good news for multiple reads. 
\end{itemize}

@@

% Ideas for the future: measure the actual amount of consumed memory.
